Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-10-31 manuscript/manuscript.tex
Minor edit to paper title
Specific aim of the paper written out

\title{Predicting Diabetes Based on Various Factors}
\author{Ashley Merritt\\
    Department of Statistics\\
    University of Connecticut
    }

@@

>>>>

\title{Predicting Diabetes Based on Various Factors Using logistic Regression}
\author{Ashley Merritt\\
    Department of Statistics\\
    University of Connecticut
    }

@@

In this paper the specific research question that I will be focusing on is: how can we use machine learning models in order to identify individuals that may have already or are at risk at developing diabetes? This will be researched using a data set that contains various metrics on one's health that will be described in the next section of the paper.
